Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-27 Paper.Rmd
it never ends

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people care more about negative cues than positive cues probably because they want to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

-   you can discuss about the fluidity of search and exp attributes

@@

-   subjectivity, emolex, heterogeneous opinions, row 10,

-   talk about the limitations as we go
-   talk about whatever we speculate we are omitting the readers buying motivation

>>>>

Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods. The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average. Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating. This means that people focus more on negative cues than positive cues probably because they want to cut down potential sure losses. A similar result was reflected by the negative coefficient of the proportion of positive words in a review. This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers. Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014]. An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021]. The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this. A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded. Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods. A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good. That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.

@@

-   more elab is needed here

```{=html}
<!-- -->
```
-   you can discuss about the fluidity of search and exp attributes

@@

-   heterogeneous opinions, row 10,

Unexpected and different results are common in the literature of Review Helpfulness [@fan2021]. This paper and the rest of the literature suffers from certain biases that the data imposes. Many other limitations may arise from potential omitted variables.

Firstly, as @mudambi2010 pointed out that potential selection bias exist in the data. It is not possible to know how many people actually read a particular review. Additionally, there is a strong possibility that as a review gets more votes this is going to draw more attention to the particular review. This can cause a positive feedback loop and this feedback loop can increase the chances that an observation making into the sample which leads to a selection bias. To fight with this, researchers usually resorted to setting a threshold of total votes where reviews with small amount of votes were filtered out of the sample. Furthermore, a multi-level regression model was developed by @kuan2015 in order to overcome the selection bias. In the first level of the regression the researchers modeled the binary case of wheter a review gets voted or not. After what makes a review voted was established, they progressed to the next stage of modelling the review helpfulness. Along with the multi-level model results they also shared OLS results where non-voted reviews were filtered from the data. Most of the significance and coefficient signs weren't different but coefficients differed in magnitude.

Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature. Let alone different methodologies, even the utilizations of similar variables were contrasting. For instance, review extremity was employed in three different ways by researchers. This paper and some others use review ratings as it is. Another group of studies took the differences of review ratings from the mean rating of a given product. This is usually called Review Inconsistency. The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5). In some studies these dummy variables were extended to negative and positive extreme dummies as well. The differences isn't limited to Review Rating. The usages the dependent variable, Perceived Helpfulness, diverged as well. In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression. Furthermore, some studies converted the percentage of the helpfulness into a binary problem where over 50% helpfulness score was considered as a helpful review. As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well. All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.

-   talk about the limitations as we go, selection bias and omitted variables, different utilizations of variables,

-   talk about whatever we speculate we are omitting the readers buying motivation, their trust towards strangers, search/exp classification is too simple,
